How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
fixed last typo
NM

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
\caption{
The permeability and anisotropy of the same 80-body simulation featured in Figures~\ref{fig1} and~\ref{fig2}. a) Both the longitudinal (solid) and transverse (dashed) permeability increase over time as the bodies erode. Also shown is the longitudinal and transverse permeabilities of the corresponding configurations of circles, which allows us to extract the configurational component of anisotropy. b) The anisotropy of the medium increases as the bodies erode and preferentially allow flow in the longitudinal direction. The total anisotropy is the sum \todo[inline]{do you mean product} of configurational and shape components. The shape contribution is larger throughout most of the simulation, but near the end of the simulation, the configurational contribution grows large as the channel-structure dominates.
\label{fig3}
}
\end{figure*}
%---------------------------------------------------------%
% Data from 80-4
%c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium. Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.

@@

As discussed in Section~\ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large scale. As detailed in Section~\ref{subsec:anis}, the configurational anisotropy can be extracted through a process in which, at any point in time, the configuration of partially-eroded bodies is replaced with a collection of circles having the same areas and centers of mass. We perform this process and show in Figure~\ref{fig3}(a) the permeabilities, $k_{11}^{(c)}$ and $k_{22}^{(c)}$, of the corresponding circle configurations. As seen in the figure, the permeabilities of the circle configurations always lie in between the values, $k_{11}$ and $k_{22}$, of the true, eroded medium. The {\em configurational} anisotropy is then computed as the permeability ratio of the circle configuration, $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$, and then the {\em shape} anisotropy can be determined through $\anis_S = \anis/\anis_C$. As seen in Figure~\ref{fig3}(b), the shape anisotropy is the larger factor throughout the majority of the simulation, implying that the shape of individual grains plays a larger role than their relative positions. It is only during the last 10\% of the simulation that the configurational anisotropy grows significantly and surpasses the shape anisotropy. This relative growth of the configurational anisotropy corresponds to the strong channelization seen in the last panel of Figure~\ref{fig1}.

>>>>

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
\caption{
The permeability and anisotropy of the same 80-body simulation featured in Figures~\ref{fig1} and~\ref{fig2}. a) Both the longitudinal (solid) and transverse (dashed) permeability increase over time as the bodies erode. Also shown is the longitudinal and transverse permeabilities of the corresponding configurations of circles, which allows us to extract the configurational component of anisotropy. b) The anisotropy of the medium increases as the bodies erode and preferentially allow flow in the longitudinal direction. The total anisotropy is the product of configurational and shape components. The shape contribution is larger throughout most of the simulation, but near the end of the simulation, the configurational contribution grows large as the channel-structure dominates.
\label{fig3}
}
\end{figure*}
%---------------------------------------------------------%
% Data from 80-4

@@

As discussed in Section~\ref{subsec:anis}, the anisotropy of the medium results from the combination of {\em shape} anisotropy, at the individual grain level, and {\em configurational anisotropy}, at the large scale. As detailed in Section~\ref{subsec:anis}, the configurational anisotropy can be extracted through a process in which, at any point in time, the configuration of partially-eroded bodies is replaced with a collection of circles having the same areas and centers of mass. We perform this process and show in Figure~\ref{fig3}(a) the permeabilities, $k_{11}^{(c)}$ and $k_{22}^{(c)}$, of the corresponding circle configurations. As seen in the figure, the permeabilities of the circle configurations always lie in between the values, $k_{11}$ and $k_{22}$, of the true, eroded medium. The {\em configurational} anisotropy is then computed as the permeability ratio of the circle configuration, $\anis_C = k_{11}^{(c)} / k_{22}^{(c)}$, and then the {\em shape} anisotropy can be determined through $\anis_S = \anis/\anis_C$. As seen in Figure~\ref{fig3}(b), the shape anisotropy is the larger factor throughout the majority of the simulation, implying that the shape of individual grains plays a larger role than their relative positions. It is only during the last 20\% of the simulation that the configurational anisotropy grows significantly and surpasses the shape anisotropy. This relative growth of the configurational anisotropy corresponds to the strong channelization seen in the last panel of Figure~\ref{fig1}.
